---
title: 'RQ1 Forest Definition Visualisations'
author: "Nina Moffat"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Information about visualisations

In this R Markdown script, I create some of the visualisations which I plan to include in my thesis. Others are created in the main Jupyter Notebook files or non-programatically using QGIS.

In this Rmd I create the following visualisations:
1. Bar chart for total forest in the Germany Natura 2000 sites per Forest/Non-forest (FNF) map.
2. Bar chart for total area in the Germany Natura 2000 sites according to the forest consensus class.
3. A multi-plot figure with 6 treemaps (1 overall, 5 for each class from 1-5) for showing which FNF maps tend to agree with each other and which do not.


```{r install}

# Install pacman for package management
library(pacman)

# Install/load required packages
p_load(tidyverse, 
       scales,
       treemap,
       ggfittext,
       cowplot,
       install = TRUE)

```


## FNF Visualisations

First I create a bar chart of the total forest per FNF map (i.e. per forest product definition/operationalisation). I also show the mean across the 6 products with a dashed line.

```{r fnf_prep}

# Adjust how many digits to display
options(digits=9)

# Read in CSV with adjusted column names
fnf_all <- read_csv("outputs/all_fnf_natura_stats.csv", 
                    col_names = c("index", 
                                  "fnf_map", 
                                  "total_forest_ha",
                                  "total_forest_per",
                                  "diff_mean_ha",
                                  "diff_mean_per"
                                  ),
                    show_col_types = FALSE
                    )

# Tidy-up: remove the first column (index) and first row (old column names)
fnf_all <- fnf_all[2:7,2:6]

# Convert columns to numeric
fnf_all$total_forest_ha <- as.numeric(fnf_all$total_forest_ha)
fnf_all$total_forest_per <- as.numeric(fnf_all$total_forest_per)
fnf_all$diff_mean_ha <- as.numeric(fnf_all$diff_mean_ha)
fnf_all$diff_mean_per <- as.numeric(fnf_all$diff_mean_per)

# Calculate the mean amount of forest (ha) across all FNF maps
fnf_mean_ha <- mean(as.numeric(fnf_all$total_forest_ha))

```


Resources for ggplot styling:
https://ggplot2.tidyverse.org/articles/faq-axes.html 
https://ggplot2-book.org/themes#sec-themes


```{r fnf_bar}

# Define the order I want the bars in
fnf_order = c("H/I", "ESA", "JAX",
              "COR", "DE", "FAO")

# Create a bar chart of the total forest, with the mean as dashed-line
ggplot(data=fnf_all, aes(x=factor(fnf_map, fnf_order), y=total_forest_ha/1000000)) +
  geom_bar(stat="identity", 
           colour="black", 
           fill="#0F5726",
           width=0.4
           )+
  labs(x="\nForest product", 
       y="Total forest area \n(millions ha)\n"
       ) +
  coord_cartesian(ylim=c(2.0, 3.1)) +
  scale_y_continuous(labels = label_number(accuracy = 0.01),
                     breaks = c(2.0, 2.25, 2.5, 2.75, 3.0),
                     ) +
  geom_hline(yintercept = fnf_mean_ha/1000000, 
             colour = "#676767", 
             linetype = 'dashed'
             ) +
  annotate("text", x=0.5, y=2.856, 
           label="Mean forest area", 
           colour="#676767",
           size = 3.5,
           hjust = 0,
           ) +
  annotate("text", x=0.835, y=2.655, 
           label="-7.14%*", 
           colour="#676767",
           size = 3,
           hjust = 0,
           ) +
  annotate("text", x=1.819, y=2.895, 
           label="+1.60%", 
           colour="#676767",
           size = 3,
           hjust = 0,
           ) +
  annotate("text", x=2.821, y=2.906, 
           label="+1.98%", 
           colour="#676767",
           size = 3,
           hjust = 0,
           ) +
  annotate("text", x=3.837, y=2.788, 
           label="-0.42%", 
           colour="white",
           size = 3,
           hjust = 0,
           ) +
  annotate("text", x=4.832, y=2.863, 
           label="+0.45%", 
           colour="#676767",
           size = 3,
           hjust = 0,
           ) +
  annotate("text", x=5.825, y=2.942, 
           label="+3.20%", 
           colour="#676767",
           size = 3,
           hjust = 0,
           ) +
  theme(panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text = element_text(size=12),
        axis.title = element_text(size=13),
        axis.title.x = element_text(vjust=4),
        axis.title.y = element_text(vjust=-3),
        #text = element_text(family="sans-serif")
        ) 


```
**NOTE**
Some times the proportions may look off in the rmd version of the figure - it will look a bit different in the saved png.


```{r fnf_save}

# Once happy with the outputs, save them! 
# Note this will output whatever plot was run last!
ggsave("outputs/figures/rq1_fnf_all_bar_chart.png",
       width=8,
       height=5
       )

```


## Forest Consensus Visualisations

In this section I create a bar chart of total area of the Germany Natura 2000 sites within each consensus class from the forest presence/absence consensus map.


```{r con_prep}

# Adjust how many digits to display
options(digits=9)

# Read in CSV with adjusted column names
consensus_all <- read_csv("outputs/all_consensus_natura_stats.csv", 
                          col_names = c("index", 
                                        "class", 
                                        "total_area_ha",
                                        "coverage_per"
                                        ),
                          show_col_types = FALSE
                          )

# Tidy-up: remove the first two columns (index) and first row (old column names)
consensus_all <- consensus_all[2:8,2:4]

# Add new class information (just want to visualise it differently)
consensus_all$forest_nonforest = c("Non-forest", "Non-forest", "Non-forest",
                                   " ", "Forest", "Forest", "Forest")
consensus_all$consensus = c("Full", "High", "Low", "None", 
                            "Low", "High", "Full")


# Convert columns to numeric
consensus_all$total_area_ha <- as.numeric(consensus_all$total_area_ha)
consensus_all$coverage_per <- as.numeric(consensus_all$coverage_per)


```


Note the colours here are selected in order to be consistent with the consensus map itself. I used a colour-blind safe palette (https://color.adobe.com/create/color-accessibility) with aim to highlight non-consensus areas compared to consensus forest. 


```{r con_bar}

# Create the bar chart for the consensus map results
ggplot(data=consensus_all, aes(x = interaction(consensus, class), 
                               y = total_area_ha/1000000,
                               fill = class)) +
  geom_bar(stat="identity",
           colour="black",
           width=0.5) +
  scale_fill_manual(values=c("#FFFFFF", "#DCDCDC", "#B4B6BB", "#F1AB4A",
                             "#EFF171", "#ABE071", "#0F5726")) +
  coord_cartesian(xlim = c(0.5, 7.5), ylim = c(0, 2.75),  expand=FALSE, clip="off") +
  scale_y_continuous(labels = label_number(accuracy = 0.1),
                     breaks = c(0, 0.5, 1.0, 1.5, 2.0, 2.5),
                     ) +
  labs(y="Total area \n(millions ha)\n") +
  annotate(geom = "text", 
           x = seq_len(nrow(consensus_all)), 
           y = -0.1, 
           label = consensus_all$consensus, 
           size = 4) +
  annotate(geom = "text", 
           x = c(2, 4, 6), 
           y = 2.5, 
           label = unique(consensus_all$forest_nonforest), 
           size = 4) +
    annotate(geom = "text", 
           x = 4, 
           y = -0.3, 
           label = "\nDegree of consensus", 
           size = 4.5) +
  geom_vline(xintercept = 3.5, 
             colour = "#676767", 
             linetype = 'dashed'
             ) +
    geom_vline(xintercept = 4.5, 
             colour = "#676767", 
             linetype = 'dashed'
             ) +
      annotate("text", x=0.757, y=1.085, 
           label="37.97%", 
           colour="black",
           size = 3,
           hjust = 0
           ) +
        annotate("text", x=1.818, y=0.175, 
           label="5.91%", 
           colour="black",
           size = 3,
           hjust = 0
           ) +
          annotate("text", x=2.818, y=0.085, 
           label="2.98%", 
           colour="black",
           size = 3,
           hjust = 0
           ) +
          annotate("text", x=3.813, y=0.071, 
           label="2.53%", 
           colour="black",
           size = 3,
           hjust = 0
           ) +
          annotate("text", x=4.818, y=0.089, 
           label="3.37%", 
           colour="black",
           size = 3,
           hjust = 0
           ) +
          annotate("text", x=5.819, y=0.25, 
           label="9.07%", 
           colour="black",
           size = 3,
           hjust = 0
           ) +
          annotate("text", x=6.762, y=1.1, 
           label="38.18%", 
           colour="white",
           size = 3,
           hjust = 0
           ) +
  theme(plot.margin = unit(c(1, 1, 3, 1), "lines"),
        panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #text = element_text(family="serif"),
        legend.position = "none",
        axis.text = element_text(size=12),
        axis.title = element_text(size=13)
        )

```


**NOTE**
Some times the proportions may look off in the rmd version of the figure - it will look a bit different in the saved png.


```{r con_bar_save}

# Once happy with the outputs, save them!
# Note this will output whatever plot was run last!
ggsave("outputs/figures/rq1_consensus_bar_chart.png",
       width=7,
       height=4
       )

```


## Treemap visualisations

In the next section I compare which forest definitions (FNF maps) agree with each other for the different consensus classes.

Resources for treemaps and multi-plot figures:
https://www.data-to-viz.com/graph/treemap.html
https://r-graph-gallery.com/treemap.html
https://wilkelab.org/cowplot/articles/plot_grid.html

First I create the main treemap which simply shows a breakdown of the classes overall (i.e. the size of the boxes in the treemap are according to the amount of area in that class). In the subsequent steps I create treemaps for class 1-5 (I skip class 0 and 6 as in these classes all the forest maps agree on either non-forest or forest, respectively). The final step is to combine all treemaps into a single, multi-plot figure.


```{r con_treemap}

# Add grouping variable name
consensus_all$treemap_group = c("Non-Forest: Full Consensus", "Non-Forest: High Consensus",
                                "Non-Forest: Low Consensus", "Uncertain: No Consensus", 
                                "Forest: Low Consensus", "Forest: High Consensus", 
                                "Forest: Full Consensus")

# Create tree map
main_tree <- treemap(consensus_all,
                     index= "treemap_group",
                     vSize="total_area_ha",
                     type="index",
                     title = ""
                     )

# Prepare tree map output for ggplot
main_tree_data <- main_tree[["tm"]] %>% 
  as_tibble() %>% 
  arrange(desc(vSize)) %>% 
  mutate(rank = row_number(),
         xmax = x0 + w,
         ymax = y0 + h
         )

# Convert tree map to ggplot plot
main_tree_plt <- ggplot(main_tree_data) +
  geom_rect(aes(xmin = x0,
                ymin = y0,
                xmax = xmax,
                ymax= ymax,
                fill = color),
            linewidth = 1,
            colour = "#1E1D23",
            fill = c("#0F5726", "#FFFFFF", "#ABE071",
                     "#DCDCDC", "#F1AB4A",  "#EFF171","#B4B6BB"),
            alpha = 0.9) +
  geom_fit_text(data = main_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = treemap_group),
                colour = "black",
                size = c(20, 12, 10, 10, 10, 10, 8),
                reflow = TRUE) + 
  labs(title = "All Consensus Categories") +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5)
        )

main_tree_plt

```


In the next section I set up the controls for the naming and colour palette generation.


```{r treemap_prep}

# Create the abbreviations for the FNF maps here
# This allows me to change them more easily in the future (only need to change here)
hansen <- "H/I"
esa <- "ESA"
jaxa <- "JAX"
corine <- "COR"
ger <- "DE"
fao <- "FAO"

# Define the separating character(s)
sep=", "

# Define an overall palette to extract colours from 
# Note I check the palette for colour blind safeness here: 
# https://color.adobe.com/create/color-accessibility
palette = c("#374CD1", "#4468FA", "#6792FA", "#81BFF5", "#A8E8F5", "#E1F0EC",
            "#F0EEAE", "#EBDF71", "#F5C43E", "#F0A021", "#C36300"
            )

# Subsections of main palette for classes with less than 11 colours
class1_pal = c(palette[1], palette[4], palette[7], palette[11])
class2_pal = c(palette[1], palette[3], palette[4], palette[6], 
               palette[7], palette[8], palette[9], palette[11])
# class3_pal not needed (full palette used)
class4_pal = c(palette[1], palette[3], palette[4], palette[5], palette[6], 
               palette[7], palette[8], palette[9], palette[10], palette[11])
class5_pal = c(palette[1], palette[4], palette[6], palette[7], palette[11])

# New palette testing
class1_pal_new = c("#B0B0B0", "#C4C4C4", "#D9D9D9", "#F2F2F2")
class2_pal_new = c("#616161", "#707070", "#7D7D7D", "#8C8C8C", 
                   "#9E9E9E", "#B0B0B0", "#C4C4C4", "#D9D9D9")
class3_pal_new = c("#b13b05", "#c84c09", "#cc560c",
                   "#e06b13", "#ef821e", "#fe9929",
                   "#feb351", "#fecc7a", "#fee19c", 
                   "#fff0b8", "#fffacb")
class4_pal_new = c("#ffd500", "#ffda0b", "#ffe121", "#ffe83b", "#ffef61",
                   "#fff384", "#fff7a3", "#fffabe", "#fffcd8", "#fffeef")
class5_pal_new = c("#78c679", "#9dd689", "#c2e699", "#e1f3b3", "#f1ffe3")
  
  
```


Now I generate the treemap figure for class 1 (i.e. which FNF maps agree on non-forest)


```{r con_treemap_class1}

# Adjust how many digits to display
options(digits=9)

# Read in CSV with adjusted column names
class1_fnf_combo <- read_csv("outputs/treemap_class1_fnfcombo_natura_stats.csv", 
                             col_names = c("index", 
                                           "fnf_combo", 
                                           "forest_pixels",
                                           "forest_area_ha"
                                           ),
                             show_col_types = FALSE
                             )

# Tidy-up: remove the first column (index) and first row (old column names)
class1_fnf_combo <- class1_fnf_combo[2:7,2:4]

# Convert columns to numeric
class1_fnf_combo$forest_pixels <- as.numeric(class1_fnf_combo$forest_pixels)
class1_fnf_combo$forest_area_ha <- as.numeric(class1_fnf_combo$forest_area_ha)

# Add labels for main category names
# For class 1, these correspond to the maps which agree on non-forests
class1_fnf_combo$fnf_combo_main = c(paste(hansen, esa, jaxa, corine, ger, sep=sep),
                                    paste(hansen, esa, jaxa, corine, fao, sep=sep),
                                    paste(hansen, esa, jaxa, ger, fao, sep=sep),
                                    paste(esa, jaxa, corine, ger, fao, sep=sep),
                                    paste(hansen, esa, corine, ger, fao, sep=sep),
                                    paste(hansen, jaxa, corine, ger, fao, sep=sep)
                                    ) 

# Add labels for sub category names
# For class 1, these correspond to the maps which agree on forests
class1_fnf_combo$fnf_combo_sub = c(fao,
                                   ger,
                                   corine,
                                   hansen,
                                   jaxa,
                                   esa
                                   ) 
  
```


```{r con_treemap_class1_plt}

# Create tree map
class1_tree <- treemap(class1_fnf_combo,
                       index= c("fnf_combo_main", "fnf_combo_sub"),
                       vSize="forest_area_ha",
                       type="index",
                       title = "",
                       )

# Prepare tree map output for ggplot
class1_tree_data <- class1_tree[["tm"]] %>% 
  as_tibble() %>% 
  arrange(desc(vSize)) %>% 
  mutate(rank = row_number(),
         xmax = x0 + w,
         ymax = y0 + h
         ) %>%
  drop_na(fnf_combo_sub)

# Convert tree map to ggplot plot
class1_tree_plt <- ggplot(class1_tree_data) +
  geom_rect(aes(xmin = x0,
                ymin = y0,
                xmax = xmax,
                ymax= ymax,
                fill = color),
            linewidth = 1,
            colour = "#1E1D23",
            fill = class1_pal_new,
            alpha = 0.9) +
  geom_fit_text(data = class1_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_main),
                colour = "black",
                size = c(20, 12, 12, 10),
                reflow = TRUE) + 
  geom_fit_text(data = class1_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_sub),
                place = "bottomright",
                colour = "black",
                size = c(16, 10, 10, 8),
                reflow = TRUE) + 
  labs(title = "Non-Forest: High Consensus") +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5)
        )

class1_tree_plt

```


The ESA map is most likely to estimate forest presence in areas where the other maps estimate non-forest.

Now I generate the treemap figure for class 2 (i.e. which FNF maps agree on non-forest)


```{r con_treemap_class2}

# Read in CSV with adjusted column names
class2_fnf_combo <- read_csv("outputs/treemap_class2_fnfcombo_natura_stats.csv", 
                             col_names = c("index", 
                                           "fnf_combo", 
                                           "forest_pixels",
                                           "forest_area_ha"
                                           ),
                             show_col_types = FALSE
                             )

# Tidy-up: remove the first column (index) and first row (old column names)
class2_fnf_combo <- class2_fnf_combo[2:16,2:4]

# Convert columns to numeric
class2_fnf_combo$forest_pixels <- as.numeric(class2_fnf_combo$forest_pixels)
class2_fnf_combo$forest_area_ha <- as.numeric(class2_fnf_combo$forest_area_ha)

# Add labels for main category names
# For class 2, these correspond to the maps which agree on non-forests
class2_fnf_combo$fnf_combo_main = c(paste(hansen, esa, jaxa, ger, sep=sep),
                                    paste(hansen, esa, jaxa, fao, sep=sep),
                                    paste(esa, jaxa, ger, fao, sep=sep),
                                    paste(hansen, jaxa, ger, fao, sep=sep),
                                    paste(hansen, jaxa, corine, ger, sep=sep),
                                    paste(hansen, jaxa, corine, fao, sep=sep),
                                    paste(jaxa, corine, ger, fao, sep=sep),
                                    paste(hansen, corine, ger, fao, sep=sep),
                                    paste(hansen, esa, jaxa, corine, sep=sep),
                                    paste(esa, jaxa, corine, fao, sep=sep),
                                    paste(esa, jaxa, corine, ger, sep=sep),
                                    paste(hansen, esa, ger, fao, sep=sep),
                                    paste(hansen, esa, corine, ger, sep=sep),
                                    paste(hansen, esa, corine, fao, sep=sep),
                                    paste(esa, corine, ger, fao, sep=sep)
                                    ) 

# Add labels for sub category names
# For class 2, these correspond to the maps which agree on forests
class2_fnf_combo$fnf_combo_sub = c(paste(corine, fao, sep=sep),
                                   paste(corine, ger, sep=sep),
                                   paste(corine, hansen, sep=sep),
                                   paste(esa, corine, sep=sep),
                                   paste(esa, fao, sep=sep),
                                   paste(esa, ger, sep=sep),
                                   paste(esa, hansen, sep=sep),
                                   paste(esa, jaxa, sep=sep),
                                   paste(ger, fao, sep=sep),
                                   paste(ger, hansen, sep=sep),
                                   paste(hansen, fao, sep=sep),
                                   paste(jaxa, corine, sep=sep),
                                   paste(jaxa, fao, sep=sep),
                                   paste(jaxa, ger, sep=sep),
                                   paste(jaxa, hansen, sep=sep)
                                   ) 

```


```{r con_treemap_class2_plt}

# Create tree map
class2_tree <- treemap(class2_fnf_combo,
                       index= c("fnf_combo_main", "fnf_combo_sub"),
                       vSize="forest_area_ha",
                       type="index",
                       title = "",
                       )

# Prepare tree map output for ggplot
class2_tree_data <- class2_tree[["tm"]] %>% 
  as_tibble() %>% 
  arrange(desc(vSize)) %>% 
  mutate(rank = row_number(),
         xmax = x0 + w,
         ymax = y0 + h
         ) %>%
  drop_na(fnf_combo_sub)

# Convert tree map to ggplot plot
class2_tree_plt <- ggplot(class2_tree_data) +
  geom_rect(aes(xmin = x0,
                ymin = y0,
                xmax = xmax,
                ymax= ymax,
                fill = color),
            linewidth = 1,
            colour = "#1E1D23",
            fill = class2_pal_new,
            alpha = 0.9) +
  geom_fit_text(data = class2_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_main),
                colour = "black",
                size = c(20, 12, 12, 12, 12, 10, 8, 8),
                reflow = TRUE) + 
  geom_fit_text(data = class2_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_sub),
                place = "bottomright",
                colour = "black",
                size = c(16, 10, 10, 10, 10, 8, 6, 6),
                reflow = TRUE) + 
  labs(title = "Non-Forest: Low Consensus") +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5)
        )

class2_tree_plt

```


Now I generate the treemap figure for class 3 (i.e. which FNF maps agree on forest - in this class there's an even split)


```{r con_treemap_class3}

# Adjust how many digits to display
options(digits=9)

# Read in CSV with adjusted column names
class3_fnf_combo <- read_csv("outputs/treemap_class3_fnfcombo_natura_stats.csv", 
                             col_names = c("index", 
                                           "fnf_combo", 
                                           "forest_pixels",
                                           "forest_area_ha"
                                           ),
                             show_col_types = FALSE
                             )

# Tidy-up: remove the first column (index) and first row (old column names)
class3_fnf_combo <- class3_fnf_combo[2:21,2:4]

# Convert columns to numeric
class3_fnf_combo$forest_pixels <- as.numeric(class3_fnf_combo$forest_pixels)
class3_fnf_combo$forest_area_ha <- as.numeric(class3_fnf_combo$forest_area_ha)

# Add labels for main category names
# For class 3, these correspond to the maps which agree on forests
class3_fnf_combo$fnf_combo_main = c(paste(corine, ger, fao, sep=sep),
                                    paste(jaxa, hansen, ger, sep=sep),
                                    paste(jaxa, hansen, fao, sep=sep),
                                    paste(jaxa, hansen, corine, sep=sep),
                                    paste(jaxa, ger, fao, sep=sep),
                                    paste(jaxa, corine, ger, sep=sep),
                                    paste(jaxa, corine, fao, sep=sep),
                                    paste(hansen, ger, fao, sep=sep),
                                    paste(hansen, corine, ger, sep=sep),
                                    paste(hansen, corine, fao, sep=sep),
                                    paste(esa, jaxa, hansen, sep=sep),
                                    paste(esa, jaxa, ger, sep=sep),
                                    paste(esa, jaxa, fao, sep=sep),
                                    paste(esa, jaxa, corine, sep=sep),
                                    paste(esa, hansen, ger, sep=sep),
                                    paste(esa, hansen, fao, sep=sep),
                                    paste(esa, hansen, corine, sep=sep),
                                    paste(esa, ger, fao, sep=sep),
                                    paste(esa, corine, ger, sep=sep),
                                    paste(esa, corine, fao, sep=sep)
                                    )

# Add labels for sub category names
# For class 3, these correspond to the maps which agree on non-forests
class3_fnf_combo$fnf_combo_sub = c(paste(hansen, esa, jaxa, sep=sep),
                                   paste(esa, corine, fao, sep=sep),
                                   paste(esa, corine, ger, sep=sep),
                                   paste(esa, ger, fao, sep=sep),
                                   paste(hansen, esa, corine, sep=sep),
                                   paste(hansen, esa, fao, sep=sep),
                                   paste(hansen, esa, ger, sep=sep),
                                   paste(esa, jaxa, corine, sep=sep),
                                   paste(esa, jaxa, fao, sep=sep),
                                   paste(esa, jaxa, ger, sep=sep),
                                   paste(corine, ger, fao, sep=sep),
                                   paste(hansen, corine, fao, sep=sep),
                                   paste(hansen, corine, ger, sep=sep),
                                   paste(hansen, ger, fao, sep=sep),
                                   paste(jaxa, corine, fao, sep=sep),
                                   paste(jaxa, corine, ger, sep=sep),
                                   paste(jaxa, ger, fao, sep=sep),
                                   paste(hansen, jaxa, corine, sep=sep),
                                   paste(hansen, jaxa, fao, sep=sep),
                                   paste(hansen, jaxa, ger, sep=sep)
                                   )

```



```{r con_treemap_class3_plt}

# Create tree map
class3_tree <- treemap(class3_fnf_combo,
                       index= c("fnf_combo_main", "fnf_combo_sub"),
                       vSize="forest_area_ha",
                       type="index",
                       title = "",
                       )

# Prepare tree map output for ggplot
class3_tree_data <- class3_tree[["tm"]] %>% 
  as_tibble() %>% 
  arrange(desc(vSize)) %>% 
  mutate(rank = row_number(),
         xmax = x0 + w,
         ymax = y0 + h
         ) %>%
  drop_na(fnf_combo_sub)

# Convert tree map to ggplot plot
class3_tree_plt <- ggplot(class3_tree_data) +
  geom_rect(aes(xmin = x0,
                ymin = y0,
                xmax = xmax,
                ymax= ymax,
                fill = color),
            linewidth = 1,
            colour = "#1E1D23",
            fill = class3_pal_new,
            alpha = 0.9) +
  geom_fit_text(data = class3_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_main),
                colour = "black",
                size = c(20, 12, 10, 8, 8, 8, 8, 8, 6, 6, 4),
                reflow = TRUE) + 
  geom_fit_text(data = class3_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_sub),
                place = "bottomright",
                colour = "black",
                size = c(16, 10, 8, 6, 6, 6, 6, 6, 4, 4, 3),
                reflow = TRUE) + 
  labs(title = "Uncertain: No Consensus") +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5)
        )

class3_tree_plt

```


Now I generate the treemap figure for class 4 (i.e. which FNF maps agree on forest)


```{r con_treemap_class4}

# Adjust how many digits to display
options(digits=9)

# Read in CSV with adjusted column names
class4_fnf_combo <- read_csv("outputs/treemap_class4_fnfcombo_natura_stats.csv", 
                             col_names = c("index", 
                                           "fnf_combo", 
                                           "forest_pixels",
                                           "forest_area_ha"
                                           ),
                             show_col_types = FALSE
                             )

# Tidy-up: remove the first column (index) and first row (old column names)
class4_fnf_combo <- class4_fnf_combo[2:16,2:4]

# Convert columns to numeric
class4_fnf_combo$forest_pixels <- as.numeric(class4_fnf_combo$forest_pixels)
class4_fnf_combo$forest_area_ha <- as.numeric(class4_fnf_combo$forest_area_ha)

# Add labels for main category names
# For class 4, these correspond to the maps which agree on forests
class4_fnf_combo$fnf_combo_main = c(paste(esa, jaxa, corine, hansen, sep=sep),
                                    paste(esa, jaxa, ger, hansen, sep=sep),
                                    paste(esa, jaxa, hansen, fao, sep=sep),
                                    paste(esa, jaxa, corine, ger, sep=sep),
                                    paste(esa, jaxa, corine, fao, sep=sep),
                                    paste(esa, jaxa, ger, fao, sep=sep),
                                    paste(esa, hansen, corine, ger, sep=sep),
                                    paste(esa, hansen, corine, fao, sep=sep),
                                    paste(esa, hansen, ger, fao, sep=sep),
                                    paste(esa, corine, ger, fao, sep=sep),
                                    paste(jaxa, hansen, corine, ger, sep=sep),
                                    paste(jaxa, hansen, corine, fao, sep=sep),
                                    paste(jaxa, hansen, ger, fao, sep=sep),
                                    paste(jaxa, corine, ger, fao, sep=sep),
                                    paste(corine, hansen, ger, fao, sep=sep)
                                    )

# Add labels for sub category names
# For class 4, these correspond to the maps which agree on non-forest
class4_fnf_combo$fnf_combo_sub = c(paste(ger, fao, sep=sep),
                                   paste(corine, fao, sep=sep),
                                   paste(corine, ger, sep=sep),
                                   paste(hansen, fao, sep=sep),
                                   paste(hansen, ger, sep=sep),
                                   paste(hansen, corine, sep=sep),
                                   paste(jaxa, fao, sep=sep),
                                   paste(jaxa, ger, sep=sep),
                                   paste(jaxa, corine, sep=sep),
                                   paste(hansen, jaxa, sep=sep),
                                   paste(esa, fao, sep=sep),
                                   paste(esa, ger, sep=sep),
                                   paste(esa, corine, sep=sep),
                                   paste(hansen, esa, sep=sep),
                                   paste(esa, jaxa, sep=sep)
                                   )

```



```{r con_treemap_class4_plt}

# Create tree map
class4_tree <- treemap(class4_fnf_combo,
                       index= c("fnf_combo_main", "fnf_combo_sub"),
                       vSize="forest_area_ha",
                       type="index",
                       title = "",
                       )

# Prepare tree map output for ggplot
class4_tree_data <- class4_tree[["tm"]] %>% 
  as_tibble() %>% 
  arrange(desc(vSize)) %>% 
  mutate(rank = row_number(),
         xmax = x0 + w,
         ymax = y0 + h
         ) %>%
  drop_na(fnf_combo_sub)

# Convert tree map to ggplot plot
class4_tree_plt <- ggplot(class4_tree_data) +
  geom_rect(aes(xmin = x0,
                ymin = y0,
                xmax = xmax,
                ymax= ymax,
                fill = color),
            linewidth = 1,
            colour = "#1E1D23",
            fill = class4_pal_new,
            alpha = 0.9) +
  geom_fit_text(data = class4_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_main),
                colour = "black",
                size = c(20, 12, 12, 10, 8, 8, 8, 8, 6, 4),
                reflow = TRUE) + 
  geom_fit_text(data = class4_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_sub),
                place = "bottomright",
                colour = "black",
                size = c(16, 10, 10, 8, 6, 6, 6, 6, 4, 0),
                reflow = TRUE) + 
  labs(title = "Forest: Low Consenus") +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5)
        )

class4_tree_plt

```


Now I generate the treemap figure for class 5 (i.e. which FNF maps agree on forest)


```{r con_treemap_class5}

# Adjust how many digits to display
options(digits=9)

# Read in CSV with adjusted column names
class5_fnf_combo <- read_csv("outputs/treemap_class5_fnfcombo_natura_stats.csv", 
                             col_names = c("index", 
                                           "fnf_combo", 
                                           "forest_pixels",
                                           "forest_area_ha"
                                           ),
                             show_col_types = FALSE
                             )

# Tidy-up: remove the first column (index) and first row (old column names)
class5_fnf_combo <- class5_fnf_combo[2:7,2:4]

# Convert columns to numeric
class5_fnf_combo$forest_pixels <- as.numeric(class5_fnf_combo$forest_pixels)
class5_fnf_combo$forest_area_ha <- as.numeric(class5_fnf_combo$forest_area_ha)

# Add labels for main category names
# For class 5, these correspond to the maps which agree on forests
class5_fnf_combo$fnf_combo_main = c(paste(esa, jaxa, hansen, corine, ger, sep=sep),
                                    paste(esa, jaxa, hansen, corine, fao, sep=sep),
                                    paste(esa, jaxa, hansen, ger, fao, sep=sep),
                                    paste(esa, jaxa, corine, ger, fao, sep=sep),
                                    paste(esa, hansen, corine, ger, fao, sep=sep),
                                    paste(hansen, jaxa, corine, ger, fao, sep=sep)
                                    )

# Add labels for sub category names
# For class 5, these correspond to the maps which agree on non-forest
class5_fnf_combo$fnf_combo_sub = c(fao,
                                   ger,
                                   corine,
                                   hansen,
                                   jaxa,
                                   esa
                                   )

```


```{r con_treemap_class5_plt}

# Create tree map
class5_tree <- treemap(class5_fnf_combo,
                       index= c("fnf_combo_main", "fnf_combo_sub"),
                       vSize="forest_area_ha",
                       type="index",
                       title = "",
                       )

# Prepare tree map output for ggplot
class5_tree_data <- class5_tree[["tm"]] %>% 
  as_tibble() %>% 
  arrange(desc(vSize)) %>% 
  mutate(rank = row_number(),
         xmax = x0 + w,
         ymax = y0 + h
         ) %>%
  drop_na(fnf_combo_sub)

# Convert tree map to ggplot plot
class5_tree_plt <- ggplot(class5_tree_data) +
  geom_rect(aes(xmin = x0,
                ymin = y0,
                xmax = xmax,
                ymax= ymax,
                fill = color),
            linewidth = 1,
            colour = "#1E1D23",
            fill = class5_pal_new,
            alpha = 0.9) +
  geom_fit_text(data = class5_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_main),
                colour = "black",
                size = c(20, 12, 12, 10, 4),
                reflow = TRUE) + 
  geom_fit_text(data = class5_tree_data,
                aes(xmin = x0, 
                    xmax = xmax, 
                    ymin = y0,
                    ymax = ymax,
                    label = fnf_combo_sub),
                place = "bottomright",
                colour = "black",
                size = c(16, 10, 10, 8, 3),
                reflow = TRUE) + 
  labs(title = "Forest: High Consensus") +
  theme_void() +
  theme(legend.position = "none",
        plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5)
        )

class5_tree_plt

```


Finally, I generate a figure with all the treemaps together. **NOTE:** This will look messy in the Rmd outputs - check the saved output figure in the next step to see what it really looks like.  


```{r all_treemaps}

# Use cowplot to assemble tree maps into one figure
plot_grid(main_tree_plt, class1_tree_plt, 
          class2_tree_plt, class3_tree_plt, 
          class4_tree_plt, class5_tree_plt, 
          ncol = 3
          ) +
  theme(plot.background = element_rect(fill = "white", colour = NA))

```


```{r all_treemaps_save}

# Once happy with the outputs, save them!
# Note this will output whatever plot was run last!
ggsave("outputs/figures/rq1_treemaps.png",
       width=23,
       height=12
       )

```


